---
title: "GSE101463.03.06.3019"
author: "AY"
date: "6/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
a new data set from the Müller group was released on the 03.03.3019

There should be soon new RNA-seq fastq files to map to the dm6 genome for us. You can use the exact same conditions as last time.
Could you in addition, map the reads from another published study:
GSE101463 (11 samples)
We would like to compare their data with ours.

# Getting the published data from GEO
```{r, engine='bash', eval=FALSE}
fasterq-dump -p -e 10 --split-files -O fastqFiles SRR5828192
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828193
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828194
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828195
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828196
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828197
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828198
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828199
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828200
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828201
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828202
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828203
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828204
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828205
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828206
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828207
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828208
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828209
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828210
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828211
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828212
fasterq-dump -p -e 10  --split-files -O fastqFiles SRR5828213
```


# STAR Mapping of GSE101463

```{r, engine='bash', eval=FALSE}
ls -1 GSE101463/fastqFiles/
SRR5828192_1.fastq
SRR5828192_2.fastq
SRR5828193_1.fastq
SRR5828193_2.fastq
SRR5828194_1.fastq
SRR5828194_2.fastq
SRR5828195_1.fastq
SRR5828195_2.fastq
SRR5828196_1.fastq
SRR5828196_2.fastq
SRR5828197_1.fastq
SRR5828197_2.fastq
SRR5828198_1.fastq
SRR5828198_2.fastq
SRR5828199_1.fastq
SRR5828199_2.fastq
SRR5828200_1.fastq
SRR5828200_2.fastq
SRR5828201_1.fastq
SRR5828201_2.fastq
SRR5828202_1.fastq
SRR5828202_2.fastq
SRR5828203_1.fastq
SRR5828203_2.fastq
SRR5828204_1.fastq
SRR5828204_2.fastq
SRR5828205_1.fastq
SRR5828205_2.fastq
SRR5828206_1.fastq
SRR5828206_2.fastq
SRR5828207_1.fastq
SRR5828207_2.fastq
SRR5828208_1.fastq
SRR5828208_2.fastq
SRR5828209_1.fastq
SRR5828209_2.fastq
SRR5828210_1.fastq
SRR5828210_2.fastq
SRR5828211_1.fastq
SRR5828211_2.fastq
SRR5828212_1.fastq
SRR5828212_2.fastq
SRR5828213_1.fastq
SRR5828213_2.fastq
```

the samples here should be mapped to genome buold *dm6*.

```{r, engine='bash', eval=FALSE}

starIndex="/home/yeroslaviz/genomes/D_melanogaster/dm6/starIndex"

mkdir -p GSE101463/STAROutput # keep permissions

for file in `ls -1 GSE101463/fastqFiles/*_1.fastq`
do
#echo "$file"
base=$(echo $file | sed -E "s/GSE101463\/fastqFiles\/(.*)_1.fastq/\1/")
#base=$(echo $file | sed -E "s/(.*)\_1\.fastq/\1/")
echo "running STAR for file $base"
STAR --runThreadN 15 --outBAMsortingThreadN 10 --outReadsUnmapped Fastx --outSAMtype BAM SortedByCoordinate --genomeDir $starIndex --outFileNamePrefix GSE101463/STAROutput/$base --readFilesIn GSE101463/fastqFiles/$base\_1.fastq GSE101463/fastqFiles/$base\_2.fastq 
done
```


# STAR ampping of the project 95 samples

The project P95 was done here in the insitutute and should also be mapped to genome build *dm6*


```{r, engine='bash', eval=FALSE}


mkdir -p P95/STAROutput # keep permissions

for file in `ls -1 P95/conc.fastq/*.conc.R1.fastq.gz`
do
#echo "$file"
base=$(echo $file | sed -E "s/P95\/conc.fastq\/(.*).conc.R1.fastq.gz/\1/")
#base=$(echo $file | sed -E "s/(.*)\_1\.fastq/\1/")
echo "running STAR for file $base"
STAR --runThreadN 15 --outBAMsortingThreadN 10 --outReadsUnmapped Fastx --outSAMtype BAM SortedByCoordinate --readFilesCommand zcat --genomeDir $starIndex --outFileNamePrefix P95/STAROutput/$base --readFilesIn $file
done
```

# second set of files from GEO to analyze


List of files to analyze:

GSM2545903	HWT Poly-A RNA-seq rep1
GSM2545904	HWT Poly-A RNA-seq rep2
GSM2545905	HWT Poly-A RNA-seq rep3
GSM2545906	K36R Poly-A RNA-seq rep1
GSM2545907	K36R Poly-A RNA-seq rep2
GSM2545908	K36R Poly-A RNA-seq rep3
GSM2545909	HWT Nuclear RNA-seq male repA
GSM2545910	HWT Nuclear RNA-seq male repB
GSM2545911	HWT Nuclear RNA-seq male repC
GSM2545912	HWT Nuclear RNA-seq male repD
GSM2545913	HWT Nuclear RNA-seq female repA
GSM2545914	HWT Nuclear RNA-seq female repB
GSM2545915	HWT Nuclear RNA-seq female repC
GSM2545916	HWT Nuclear RNA-seq female repD
GSM2545917	K36R Nuclear RNA-seq male repA
GSM2545918	K36R Nuclear RNA-seq male repB
GSM2545919	K36R Nuclear RNA-seq male repC
GSM2545920	K36R Nuclear RNA-seq male repD
GSM2545921	K36R Nuclear RNA-seq female repA
GSM2545922	K36R Nuclear RNA-seq female repB
GSM2545923	K36R Nuclear RNA-seq female repC
GSM2545924	K36R Nuclear RNA-seq female rep

## Downloading the files

```bash
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366366
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366367
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366368
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366369
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366370
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366371
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366372
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366373
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366374
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366375
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366376
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366377
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366378
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366379
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366380
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366381
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366382
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366383
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366384
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366385
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366386
fasterq-dump -p -e 10 --split-files -O fastqFiles 	SRR5366387
```

## QC analysis

```bash
mkdir fastqcResults/
fastqc -o fastqcResults/ -t 23 fastqFiles/*.fastq
```

## Mapping with `SATR`

This uses the conda-snakemake script `Cotopaxi.Star.MappingQuant.PairedEndFastq.Snakefile` to run the Mapping-indexing-converting within the snakemake workflow.

```bash
snakemake -ps ~/poolFolders/pool-bcfngs/scripts/Cotopaxi.Star.MappingQuant.PairedEndFastq.Snakefile -j 18
```



